A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
updated formatting of graphs in discussion

library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(knitr)
library(kableExtra)
library(rstanarm)

@@

@@

## How has the Forecast Changed Over Time? {#sec-first-point}
```{r}
filtered_prediction <- prediction %>%
  filter(national_poll == 1)

@@

asdfasdfasdfasdf

## Which States Prefer Harris? {#sec-second-point}
```{r}
state_data <- prediction %>% filter(national_poll == 0)
# Identify missing data
missing_data_summary <- prediction %>%
  group_by(state) %>%
  summarize(missing_dates = sum(is.na(predicted_pct)),
            total_dates = n())

print(missing_data_summary)

@@

```{r}
# Filter to keep only the most recent entry for each state based on 'end_date'
filtered_data <- prediction %>%
  filter(!is.na(state)) %>%
  arrange(state, end_date) %>%
  group_by(state) %>%
  slice_tail(n = 1) %>%
  ungroup() %>%
  select(state, end_date, predicted_pct)

@@

>>>>

library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(knitr)
library(kable)
library(rstanarm)

@@

# Display the summary statistics in a nicely formatted table
summary_stats |>
  kable
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

@@

## How has the Forecast Changed Over Time? {#sec-first-point}

```{r}
#| label: fig-predicted-and-real
#| fig-cap: Comparison of Predicted vs Actual National Poll Percentages for Harris Over Time
#| echo: false
#| fig-width: 5 
#| fig-align: center

filtered_prediction <- prediction %>%
  filter(national_poll == 1)

@@

## Which States Prefer Harris? {#sec-second-point}

```{r}
#| label: tbl-state-missing
#| fig-cap: Summary of missing and total dates across key states
#| echo: false
#| tbl-align: center

state_data <- prediction %>% filter(national_poll == 0)
# Identify missing data
missing_data_summary <- prediction %>%
  group_by(state) %>%
  summarize(missing_dates = sum(is.na(predicted_pct)),
            total_dates = n())

# Display the summary statistics in a nicely formatted table
missing_data_summary %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

```{r}
#| label: fig-state-comparison
#| fig-cap: State-by-State comparison of predicted percentages over time
#| echo: false
#| fig-width: 5 
#| fig-align: center

@@

```{r}
#| label: fig-state-summary
#| fig-cap: Summary of Kamala Harris' predicted popular vote by key states
#| echo: false
#| fig-width: 5 
#| fig-align: center

# Filter to keep only the most recent entry for each state based on 'end_date'
filtered_data <- prediction %>%
  filter(!is.na(state)) %>%
  arrange(state, end_date) %>%
  group_by(state) %>%
  slice_tail(n = 1) %>%
  ungroup() %>%
  select(state, end_date, predicted_pct)

@@

asdfasdfasdf
